### 2023-08-08 introduction.tex
up

Safety requires that only one aircraft at a time attempts to land. The role of the control tower is to ensure this;
there are two possible choices: aircraft $A$ waits for aircraft $B$ to land
or vice-versa. To make its choice known to the aircrafts, the control tower will use the counters. 
We assume that the VASS is
lossy, i.e. 
 the contents of a counter can spontaneously get lower at any time.
\alain{contradictoire, à enlever:  Lossiness is represented by using transitions decreasing any counter by one from every state.}
% We ask however that the system is not too lossy. We add the condition that for every prefix of an execution, the number of ``lossiness transition'' for a counter is less than nine tenth of the number of transitions incrementing said counter.
In this example, the safe states would be ones where the aircrafts have both landed, i.e.
$\Safe = \{(q_{A,1}, q_{M,i}, q_{B,1})(\textbf{v}) \mid \textbf{v} \in \N^4, i \in \N\}$, and $\Bad$ is the complement of $\Safe$. 
% We remark that $\Safe$ and $\Bad$ are here both upward and downward closed.
Resilience here expresses that the aircrafts will both land, while $k$-resilience is the property insuring that they will do so in at most $k$ steps. 
%$k$-resilience is of interest since in general we want to ensure the safe space will 
%be reached in
%the least amount of steps possible. 
In this exemple, aircrafts cannot simply wait in the air an unbounded amount of time: here, $8$-resilience hold.\alain{expliquer}
\end{example}

>>>>

Safety requires that only one aircraft at a time attempts to land. The role of the control tower is to ensure this;
there are two possible choices: aircraft $A$ waits for aircraft $B$ to land
or vice-versa. To make its choice known to the aircrafts, the control tower will use the counters. 
We assume that the VASS is
lossy;  Lossiness will be represented by using transitions decreasing any counter by one from every state.
% We ask however that the system is not too lossy. We add the condition that for every prefix of an execution, the number of ``lossiness transition'' for a counter is less than nine tenth of the number of transitions incrementing said counter.
In this example, the safe states would be ones where the aircrafts have both landed, i.e.
$\Safe = \{(q_{A,1}, q_{M,i}, q_{B,1})(\textbf{v}) \mid \textbf{v} \in \N^4, i \in \N\}$, and $\Bad$ is the complement of $\Safe$. 
% We remark that $\Safe$ and $\Bad$ are here both upward and downward closed.
Resilience here expresses that the aircrafts will both land, while $k$-resilience is the property insuring that they will do so in at most $k$ steps. 
%$k$-resilience is of interest since in general we want to ensure the safe space will 
%be reached in
%the least amount of steps possible. 
In this exemple, aircrafts cannot simply wait in the air an unbounded amount of time: here, $8$-resilience hold.\alain{expliquer}
\end{example}
